\section{Research Question Evaluation}
\label{sec:reasearch-questions-evaluation}
The following list contains a discussion of the research questions from chapter \ref{ch:introduction}.

\begin{enumerate}
  \item \textbf{How to make an improved search in terms of relevance compared to TF-IDF?}
  As mentioned in section \ref{sec:problem-specification} the main focus areas were scaling and latency.
  Therefore, the relevance was never measured.
  Based on the work by Rudihagen,
  this thesis assumes that query expansion returns more relevant results compared to the baseline search.

  \item \textbf{How to develop an improved search which scales with an increasing amount of data?}
  The Elasticsearch plugin were tested with a index size of 2.3 GB,
  which is not an extreme data size in todays measure.
  The query expansion plugin were about 20 \% slower compared to the baseline search.
  As Elasticsearch have proven to scale to petabytes of data \cite{elasticsearch-scale} together with good results described earlier in this chapter,
  we can assume that the plugin would be able to scale on a larger Elasticsearch cluster.


  \item \textbf{How to delevop an improved search that fulfills the interactive latency requirements?}
  The results shows that the implementation is well within the limit for interactive tasks.
  Even when the search result size increases to 200 documents,
  the search is delivered within 54 ms on average.
  All the tests were conducted on a setup close to a real world web application,
  which indicates that the implementation also would work on an actual web application.

\end{enumerate}
